### 2013-06-28 Tex/chapters/results.tex
Tabelle für autokorr und equilibriums zeiten

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetisation per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{ssec:eqtime}).
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
\(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
random proximity graphs with the same disorder paramter \(\sigma\)
are then averaged to \(\overline{\avg{O}}\). The errors are estimated
by bootstrapping \cite{Bootstrap}.

>>>>

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetisation per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{ssec:eqtime}). The used values for different system sizes
are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
these values are generously rounded up to be on the safe side.
\begin{table}[htbp]
    \center
    \begin{tabular}{l r r r r r}
        \toprule
        \(L\)    & 16 &  32 &  64 & 128 & 256\\
        \midrule
        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
        \(t_eq\) & 40 & 100 & 100 & 200 & 600\\
        \bottomrule
    \end{tabular}
    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
    \label{tab:tauAndTeq}
\end{table}\\
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
\(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
random proximity graphs with the same disorder paramter \(\sigma\)
are then averaged to \(\overline{\avg{O}}\). The errors are estimated
by bootstrapping \cite{Bootstrap}.
